\EVOSUITE at the SBST 2018 Tool Competition

### 2018-02-28 papers/sbst18/mainTable.tex
updated scripts and paper

\begin{tabular}{ l rrrrrrr rrrrrrrr}\toprule 
 Benchmark &  \multicolumn{7}{c}{Branch Coverage} &  \multicolumn{7}{c}{Mutation Score}\\ 
 & 10s & 30s & 60s & 120s & 240s & 300s & 480s & 10s & 30s & 60s & 120s & 240s & 300s & 480s \\ 

@@

BCEL-1 & 54.7\% & 47.9\%\\ 
BCEL-10 & 62.5\% & 56.0\%\\ 
BCEL-2 & 1.2\% & 0.8\% & \multicolumn{13}{l}{Resulting test suite's coverage: 34\% (average coverage for all fitness functions)}\\ 
BCEL-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
& \multicolumn{13}{l}{org.evosuite.shaded.org.mockito.exceptions.misusing.InvalidUseOfMatchersException: 
Misplaced or misused argument matcher detected here}\\ 
BCEL-4 & 80.8\% & 80.5\%\\ 
BCEL-5 & 37.5\% & 63.8\%\\ 
BCEL-6 & 59.3\% & 76.0\%\\ 
BCEL-7 & 60.0\% & 50.0\%\\ 
BCEL-8 & 95.8\% & 90.6\%\\ 
BCEL-9 & 81.1\% & 67.5\%\\ 
FREEHEP-1 & 93.1\% & 42.2\%\\ 
FREEHEP-10 & 95.8\% & 69.6\%\\ 
FREEHEP-2 & 76.6\% & 5.7\%\\ 
FREEHEP-3 & 55.6\% & 62.1\%\\ 
FREEHEP-4 & 46.8\% & 22.2\%\\ 
FREEHEP-5 & 70.9\% & 54.1\%\\ 
FREEHEP-6 & 59.3\% & 27.0\%\\ 
FREEHEP-7 & 81.2\% & 77.2\%\\ 
FREEHEP-8 & 93.1\% & 74.7\%\\ 
FREEHEP-9 & 29.7\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%
& \multicolumn{13}{l}{Resulting test suite's coverage: 36\%; ERROR ClassStateSupport - Could not initialize org.freehep.math.minuit.ModularFunctionMinimizer}\\ 
GSON-1 & 63.9\% & 41.7\%\\ 
GSON-10 & 58.5\% & 39.0\%\\ 
GSON-2 & 33.5\% & 34.8\%\\ 
GSON-3 & 77.5\% & 81.6\%\\ 
GSON-4 & 31.4\% & 24.2\%\\ 
GSON-5 & 29.3\% & 34.8\%\\ 
GSON-6 & 86.0\% & 72.6\%\\ 
GSON-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{java.lang.RuntimeException: not implemented: class sun.reflect.generics.reflectiveObjects.TypeVariableImpl}\\ 
GSON-8 & 86.0\% & 70.2\%\\ 
GSON-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{java.lang.RuntimeException: not implemented: class sun.reflect.generics.reflectiveObjects.TypeVariableImpl}\\ 
IMAGE-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                            \cellcolor{light-gray}
                                                            \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.apache.commons.imaging.formats.tiff.write.TiffOutputDirectory: tried to access class org.apache.commons.imaging.formats.tiff.write.TiffOutputItem}\\ 
IMAGE-2 & 88.3\% & 99.0\%\\ 
IMAGE-3 & 57.0\% & 32.5\%\\ 
IMAGE-4 & 80.6\% & 73.9\%\\ 
JXPATH-1 & 27.5\% & 25.4\%\\ 
JXPATH-10 & 40.8\% & 33.5\%\\ 
JXPATH-2 & 82.6\% & 72.7\%\\ 
JXPATH-3 & 73.4\% & 83.7\%\\ 
JXPATH-4 & 78.4\% & 72.8\%\\ 
JXPATH-5 & 90.0\% & 92.9\%\\ 
JXPATH-6 & 93.5\% & 96.0\%\\ 
JXPATH-7 & 24.5\% & 10.8\%\\ 
JXPATH-8 & 52.7\% & 42.8\%\\ 
JXPATH-9 & 68.4\% & 27.9\%\\ 
LA4J-1 & 75.4\% & 81.4\%\\ 
LA4J-10 & 86.4\% & 67.9\%\\ 
LA4J-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
                                                           & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.RowMajorMatrixIterator}\\ 
LA4J-3 & 67.1\% & 37.6\%\\ 
LA4J-4 & 84.8\% & 74.7\%\\ 
LA4J-5 & 52.9\% & 34.5\%\\ 
LA4J-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray}
                                                           \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator}\\ 
LA4J-7 & 64.3\% & 40.6\%\\ 
LA4J-8 & 76.5\% & 93.6\%\\ 
LA4J-9 & 94.3\% & 30.4\%\\ 
OKHTTP-1 & 7.2\% & 5.6\%\\ 
OKHTTP-2 & 50.0\% & 44.1\%\\ 
OKHTTP-3 & 74.2\% & 67.6\%\\ 
OKHTTP-4 & 58.1\% & 53.5\%\\ 
OKHTTP-5 & 3.0\% & 4.0\%\\ 
OKHTTP-6 & 77.1\% & 76.3\%\\ 
OKHTTP-7 & 46.9\% & 27.0\%\\ 
OKHTTP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                             \cellcolor{light-gray}
                                                             \textcolor{black}{0.0}\%
 & \multicolumn{13}{l}{Caused by: java.lang.ClassNotFoundException:
   Class okio/Buffer.class should be in target project, but could not be found!}\\ 
RE2J-1 & 54.5\% & 36.9\%\\ 
RE2J-2 & 93.8\% & 71.6\%\\ 
RE2J-3 & 50.0\% & 37.9\%\\ 
RE2J-4 & 97.9\% & 90.6\%\\ 
RE2J-5 & 57.6\% & 29.1\%\\ 
RE2J-6 & 83.5\% & 71.2\%\\ 
RE2J-7 & 47.1\% & 27.8\%\\ 
RE2J-8 & 91.8\% & 79.0\%\\ 

@@

Average  &  57.9\% &  47.3\%\\ 

>>>>

\begin{tabular}{ ll rrrr rrrr}\toprule 
 \multirow{2}{1in}{Benchmark} & \multirow{2}{1in}{Java Class} &  \multicolumn{4}{c}{Branch Coverage} &  \multicolumn{4}{c}{Mutation Score}\\\cmidrule(lr){3-6}\cmidrule(lr){7-10} 
 & & 10s & 60s & 120s & 240s & 10s & 60s & 120s & 240s \\ 

@@

DUBBO-10  &  com.alibaba.dubbo.common.bytecode.Wrapper & 24.1\% & 24.5\% & 25.3\% & 28.2\% & 11.5\% & 20.9\% & 21.3\% & 20.9\%\\ 
DUBBO-2  &  com.alibaba.dubbo.common.utils.ReflectUtils & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
DUBBO-3  &  com.alibaba.dubbo.common.utils.StringUtils & 87.1\% & 94.6\% & 96.8\% & 97.1\% & 93.9\% & 87.3\% & 81.8\% & 85.8\%\\ 
DUBBO-4  &  com.alibaba.dubbo.common.utils.ClassHelper & 92.4\% & 94.4\% & 95.8\% & 95.1\% & 66.7\% & 91.4\% & 93.8\% & 92.6\%\\ 
DUBBO-5  &  com.alibaba.dubbo.common.io.UnsafeByteArrayOutputStream & 94.4\% & 94.4\% & 94.4\% & 94.4\% & 68.3\% & 77.8\% & 79.4\% & 78.9\%\\ 
DUBBO-6  &  com.alibaba.dubbo.common.utils.CompatibleTypeUtils & 4.7\% & 3.9\% & 4.7\% & 4.7\% & 3.1\% & 2.9\% & 3.1\% & 2.3\%\\ 
DUBBO-7  &  com.alibaba.dubbo.common.beanutil.JavaBeanDescriptor & 80.2\% & 92.4\% & 95.1\% & 97.9\% & 77.9\% & 96.2\% & 97.4\% & 99.0\%\\ 
DUBBO-8  &  com.alibaba.dubbo.common.Parameters & 61.1\% & 66.1\% & 77.6\% & 77.6\% & 49.5\% & 74.8\% & 76.9\% & 78.4\%\\ 
DUBBO-9  &  com.alibaba.dubbo.common.io.Bytes & 67.8\% & 71.9\% & 79.5\% & 77.1\% & 38.1\% & 65.2\% & 71.8\% & 70.4\%\\ 
FASTJSON-1  &  com.alibaba.fastjson.parser.JSONLexerBase & \cellcolor{light-gray} \textcolor{black}{-} & 15.9\% & 15.2\% & 20.4\% & \cellcolor{light-gray} \textcolor{black}{-} & 3.7\% & 6.8\% & 10.2\%\\ 
FASTJSON-10  &  com.alibaba.fastjson.serializer.StringCodec & 40.0\% & 44.2\% & 46.7\% & 50.0\% & 21.8\% & 42.0\% & 44.3\% & 45.4\%\\ 
FASTJSON-2  &  com.alibaba.fastjson.util.TypeUtils & 6.8\% & 28.7\% & 31.2\% & 40.4\% & 8.6\% & 30.3\% & 32.9\% & 43.5\%\\ 
FASTJSON-3  &  com.alibaba.fastjson.parser.DefaultJSONParser & 5.3\% & 9.3\% & 16.2\% & 18.5\% & 2.9\% & 6.8\% & 13.4\% & 16.9\%\\ 
FASTJSON-4  &  com.alibaba.fastjson.JSONArray & 20.0\% & 32.2\% & 21.1\% & 30.6\% & 34.2\% & 52.3\% & 38.7\% & 54.0\%\\ 
FASTJSON-5  &  com.alibaba.fastjson.util.JavaBeanInfo & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 15.7\% & 17.6\% & 21.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 12.2\% & 15.2\% & 17.6\%\\ 
FASTJSON-6  &  com.alibaba.fastjson.serializer.DateCodec & 18.5\% & 39.2\% & 48.0\% & 34.5\% & 8.8\% & 20.9\% & 25.9\% & 19.1\%\\ 
FASTJSON-7  &  com.alibaba.fastjson.util.IOUtils & 52.4\% & 63.6\% & 66.6\% & 71.6\% & 18.9\% & 40.2\% & 46.8\% & 49.8\%\\ 
FASTJSON-8  &  com.alibaba.fastjson.parser.JSONReaderScanner & 69.6\% & 70.1\% & 73.1\% & 77.3\% & 74.7\% & 70.6\% & 71.0\% & 73.1\%\\ 
FASTJSON-9  &  com.alibaba.fastjson.util.ASMUtils & 38.5\% & 39.1\% & 39.1\% & 39.1\% & 27.6\% & 38.6\% & 39.0\% & 39.5\%\\ 
JSOUP-1  &  org.jsoup.parser.TokenQueue & 85.8\% & 90.0\% & 90.6\% & 94.9\% & 59.3\% & 81.8\% & 85.6\% & 87.5\%\\ 
JSOUP-2  &  org.jsoup.select.QueryParser & 49.8\% & 24.9\% & 21.9\% & 55.8\% & 36.4\% & 12.8\% & 11.3\% & 40.8\%\\ 
JSOUP-3  &  org.jsoup.helper.DataUtil & 39.6\% & 38.7\% & 44.8\% & 52.0\% & 28.3\% & 28.1\% & 41.0\% & 49.8\%\\ 
JSOUP-4  &  org.jsoup.parser.Parser & 48.3\% & 95.0\% & 98.3\% & 98.0\% & 31.7\% & 80.6\% & 85.6\% & 87.3\%\\ 
JSOUP-5  &  org.jsoup.parser.Tokeniser & 35.6\% & 53.3\% & 54.8\% & 56.5\% & 23.4\% & 44.0\% & 47.3\% & 50.0\%\\ 
OKIO-1  &  okio.Buffer & 44.6\% & 42.1\% & 58.3\% & 56.1\% & 9.8\% & 21.0\% & 34.1\% & 23.9\%\\ 
OKIO-10  &  okio.Timeout & 83.3\% & 80.0\% & 85.6\% & 83.3\% & 76.8\% & 78.1\% & 82.5\% & 80.7\%\\ 
OKIO-2  &  okio.ByteString & 81.7\% & 72.3\% & 89.8\% & 95.0\% & 40.9\% & 59.2\% & 84.5\% & 78.7\%\\ 
OKIO-3  &  okio.SegmentedByteString & 56.1\% & 72.5\% & 88.9\% & 87.8\% & 28.0\% & 61.4\% & 67.6\% & 69.2\%\\ 
OKIO-4  &  okio.RealBufferedSource & 12.7\% & 27.4\% & 40.1\% & 49.9\% & 12.3\% & 17.9\% & 30.5\% & 51.1\%\\ 
OKIO-5  &  okio.RealBufferedSink & 61.4\% & 79.5\% & 89.1\% & 93.4\% & 45.7\% & 76.9\% & 86.5\% & 88.4\%\\ 
OKIO-6  &  okio.Okio & 73.2\% & 81.5\% & 82.1\% & 85.7\% & 80.6\% & 83.3\% & 83.9\% & 86.7\%\\ 
OKIO-7  &  okio.Segment & 85.4\% & 96.5\% & 97.2\% & 97.2\% & 54.5\% & 77.6\% & 78.0\% & 79.3\%\\ 
OKIO-8  &  okio.AsyncTimeout & 40.9\% & 58.0\% & 55.7\% & 59.5\% & 20.6\% & 46.1\% & 58.2\% & 60.5\%\\ 
OKIO-9  &  okio.Utf8 & 42.3\% & 42.3\% & 42.3\% & 42.3\% & 25.6\% & 35.9\% & 35.9\% & 35.9\%\\ 
REDISSON-1  &  org.redisson.RedissonSetMultimapValues & 13.3\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & 1.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\ 
REDISSON-10  &  org.redisson.config.Config & 63.8\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 97.8\% & \cellcolor{light-gray} \textcolor{black}{-} & 17.1\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 20.9\% & \cellcolor{light-gray} \textcolor{black}{-}\\ 
REDISSON-2  &  org.redisson.RedissonQueue & 39.6\% & 25.0\% & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\ 
REDISSON-3  &  org.redisson.jcache.JCacheManager & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
REDISSON-4  &  org.redisson.RedissonSetMultimap & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-}\\ 
REDISSON-5  &  org.redisson.RedissonBloomFilter & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\ 
REDISSON-6  &  org.redisson.reactive.RedissonMapReactive & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\ 
REDISSON-7  &  org.redisson.RedissonBaseMapIterator & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\ 
REDISSON-8  &  org.redisson.jcache.JCachingProvider & 58.3\% & 61.1\% & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-} & 80.6\% & 79.0\% & \cellcolor{light-gray} \textcolor{black}{-} & \cellcolor{light-gray} \textcolor{black}{-}\\ 
REDISSON-9  &  org.redisson.cluster.ClusterPartition & 68.2\% & 92.4\% & 99.2\% & 99.2\% & 30.1\% & 69.9\% & 75.5\% & 74.5\%\\ 
WEBMAGIC-1  &  us.codecraft.webmagic.model.PageModelExtractor & 10.3\% & 17.9\% & 21.5\% & 22.4\% & 24.6\% & 34.0\% & 41.0\% & 42.0\%\\ 
WEBMAGIC-2  &  us.codecraft.webmagic.Spider & 25.9\% & 36.1\% & 40.7\% & 41.5\% & 52.1\% & 60.8\% & 60.2\% & 53.6\%\\ 
WEBMAGIC-3  &  us.codecraft.webmagic.Site & 55.2\% & 65.4\% & 79.9\% & 84.1\% & 33.9\% & 90.7\% & 79.5\% & 83.2\%\\ 
WEBMAGIC-4  &  us.codecraft.webmagic.Page & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
WEBMAGIC-5  &  us.codecraft.webmagic.utils.DoubleKeyMap & 50.0\% & 26.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%} & 68.8\% & 30.0\% & \cellcolor{light-gray} \textcolor{black}{0.0\%} & \cellcolor{light-gray} \textcolor{black}{0.0\%}\\ 
ZXING-1  &  com.google.zxing.qrcode.detector.FinderPatternFinder & 29.8\% & 32.8\% & 36.3\% & 39.3\% & 4.4\% & 16.2\% & 22.8\% & 16.7\%\\ 
ZXING-10  &  com.google.zxing.qrcode.encoder.Encoder & 68.4\% & 79.6\% & 80.4\% & 81.7\% & 54.1\% & 73.7\% & 76.3\% & 73.2\%\\ 
ZXING-2  &  com.google.zxing.pdf417.decoder.PDF417ScanningDecoder & 24.3\% & 25.6\% & 27.5\% & 30.3\% & 6.8\% & 17.9\% & 27.1\% & 32.9\%\\ 
ZXING-3  &  com.google.zxing.common.StringUtils & 87.6\% & 90.8\% & 91.5\% & 91.7\% & 3.9\% & 65.5\% & 65.9\% & 68.6\%\\ 
ZXING-4  &  com.google.zxing.client.result.ResultParser & 86.2\% & 81.9\% & 89.2\% & 95.3\% & 82.0\% & 75.7\% & 83.2\% & 84.3\%\\ 
ZXING-5  &  com.google.zxing.qrcode.encoder.MatrixUtil & 46.0\% & 77.9\% & 80.0\% & 89.0\% & 53.4\% & 53.5\% & 56.8\% & 52.6\%\\ 
ZXING-6  &  com.google.zxing.datamatrix.decoder.BitMatrixParser & 36.3\% & 56.5\% & 60.5\% & 61.5\% & 45.3\% & 33.1\% & 34.4\% & 37.7\%\\ 
ZXING-7  &  com.google.zxing.pdf417.decoder.ec.ModulusPoly & 96.1\% & 97.4\% & 96.5\% & 97.4\% & 72.7\% & 87.0\% & 92.4\% & 92.4\%\\ 
ZXING-8  &  com.google.zxing.maxicode.decoder.DecodedBitStreamParser & 54.4\% & 67.2\% & 77.8\% & 82.2\% & 31.1\% & 36.9\% & 42.3\% & 46.8\%\\ 
ZXING-9  &  com.google.zxing.oned.CodaBarWriter & 89.8\% & 91.5\% & 92.5\% & 96.9\% & 52.5\% & 57.1\% & 61.0\% & 63.5\%\\ 

@@

Average &  &  47.8\% &  53.3\% &  58.9\% &  61.6\% &  34.8\% &  46.6\% &  51.4\% &  53.5\%\\ 
